\begin{acknowledgements}
    In the name of Allah, the Most Gracious and the Most Merciful.
    
    All praises to Allah for the strengths and His blessings in completing this thesis. I would like to first express my very great appreciation to my supervisor, Assoc. Prof. Dr. Zamri Zainal Abidin for his supervision, guidance, and positive reviews in this project. I would also like to thank Mr. Hassan Zakie for his assistance and advice for this project, especially in the technicalities involved. I wish to extend my thanks to all the other members of the Radio Cosmology Lab as well, for keeping the tasks exciting and fun, even in remote and online environments due to the pandemic.
    
    Special thanks to Prof. Lee Ke Jia for his guidance and practical suggestions on the project as well as keeping my progress on schedule. I'd also like to acknowledge Mr. Zhang Chun Feng for his invaluable insight in understanding the mathematical aspects and the original BEAR program itself. In addition, I appreciate all the contributions from the other members of the Pulsar Group of Peking University, as well as researchers and technicians involved in the FRB data collection, especially from the Parkes Telescope.
    
    I would like to express my gratitude to my parents who have instilled me with the love for science at an early age and have supported me ever since, for me to pursue a career in the field. Last but not least, thank you to my close friends and classmates who have given me encouragements and company throughout the project. 
\end{acknowledgements}